Self Regulation Ontology Retest Analyses

### 2018-05-17 code/SRO_Retest_Analyses.Rmd
frisem prep

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  summarise(mean_pct = mean(value),
            sd_pct = sd(value),
            n = n()) %>%
  mutate(cvl = qt(0.025, n-1),
         cvu = qt(0.975, n-1),
         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
         ciu = mean_pct+(sd_pct*cvu)/sqrt(n),
         sem_pct = sd_pct/sqrt(n)) %>%
  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance")), mean_pct, color=task))+
  geom_point(position=position_dodge(width = 0.25), size = 4)+
  # geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
  geom_errorbar(aes(ymin=cil, ymax=ciu), position=position_dodge(width = 0.25), width=0.25, size=2)+
  theme_bw()+
  xlab('')+
  ylab('Percent')+
  theme(legend.title = element_blank(),
        legend.text = element_text(size=14),
        legend.position = 'bottom',
        axis.text = element_text(size=12),
        axis.title.y = element_text(size=12))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))

ggsave('Variance_Breakdown_DotPlot.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 6, height = 5, units = "in", dpi = 100)
```

@@

tmp2 %>%
  filter(overall_difference == "overall") %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  # facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))

ggsave('PointEst_DDM_Comp_OverallOnly.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 5, units = "in", limitsize = FALSE)
```

>>>>

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  summarise(mean_pct = mean(value),
            sd_pct = sd(value, na.rm=T),
            n = n()) %>%
  mutate(cvl = qt(0.025, n-1),
         cvu = qt(0.975, n-1),
         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
         ciu = mean_pct+(sd_pct*cvu)/sqrt(n),
         sem_pct = sd_pct/sqrt(n)) %>%
  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Between subject variance",
                               "Within subject variance",
                               "Error variance")), mean_pct))+
  # geom_point(position=position_dodge(width = 0.25), size = 3, aes(color=task))+
  geom_bar(position=position_dodge(width = 0.5), width=0.5, aes(fill=task), stat='identity', alpha=0.5)+
  # geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
  geom_errorbar(aes(ymin=cil, ymax=ciu, color=task), position=position_dodge(width = 0.5), width=0.1)+
  theme_bw()+
  xlab('')+
  ylab('Percent of total variance')+
  theme(legend.title = element_blank(),
        legend.text = element_text(size=14),
        # legend.position = 'bottom',
        axis.text = element_text(size=12),
        axis.title.y = element_text(size=12))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  ylim(0,100)

ggsave('Variance_Breakdown_BarPlot.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 6, height = 5, units = "in", dpi = 300)
```

@@

tmp2 %>%
  # filter(overall_difference == "overall") %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))+
  ylim(-0.4, 1)

ggsave('PointEst_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 15, height = 7, units = "in", limitsize = FALSE)
```
